Computer Science House Constitution

### 2022-02-15 constitution.tex
Allows Active Members to propose changes to the COC

\documentclass{article}
\providecommand{\RevisionInfo}{}
\usepackage{hyperref}
% Reformat section titles
\usepackage{titlesec}
\usepackage{cleveref}

@@

\asubsubsection{Code of Conduct}
The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
\\* \\*
Members are bound to the Code of Conduct revision that they sign when initially creating their account.
Members may sign a more recent revision of the Code of Conduct to update their agreement.
\asubsubsubsection{Changes}
The following process is used for making changes to the Code of Conduct document.
\begin{enumerate}
	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
\end{enumerate}

@@

\asubsection{Guidelines on Overriding Executive Board Qualifications}
\begin{itemize}
\item This section provides no definitions, instead serving to clarify the applicability of Overrides to Qualifications in the Selection of members of the Executive Board.
\item When executing a Constitutional Override \ref{Semantic Changes} for a Qualification specified in sections {\crefname{Qualifications}{}{}\crefrange{Qualifications to be the Chairperson, Evaluations Director}{Qualifications to be the House Secretary or an Ad Hoc Director}}, the Override shall apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.
\end{itemize}

>>>>

\documentclass{article}
\providecommand{\RevisionInfo}{}
\usepackage{hyperref}
% Reformat section titles
\usepackage{titlesec}

@@

\asubsubsection{Code of Conduct}
The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
\\* \\*
Members are bound to the Code of Conduct revision that they sign when initially creating their account.
Members may sign a more recent revision of the Code of Conduct to update their agreement.
\asubsubsubsection{Changes}
The following process is used for making changes to the Code of Conduct document.
\begin{enumerate}
	\item An Active Member drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
\end{enumerate}

@@
